---
title: Atrial Fibrillation and Electrical Cardioversion
subtitle: Pilot Study
author:
  - Mina Sous
  - Anish Shah
data: "`r format(Sys.Date(), '%B %d, %Y')`"
output:
  xaringan::moon_reader:
    css: xaringan-themer.css
    self_contained: true
    nature:
      titleSlideClass: [center, middle, inverse]
      highlightLines: true
---


```{r, knitr, include=FALSE}
knitr::opts_chunk$set(
   fig.retina = 3,
   warning = FALSE,
   message = FALSE,
   echo = FALSE,
   cache = TRUE
)
```

```{r themer, echo=FALSE, include=FALSE, warning=FALSE}
library(xaringanthemer)
style_duo_accent(primary_color = "#091F40", secondary_color = "#AC1E2D")
```

```{r, targets}
tar_load(file_mina)
```


```{r}

proc <-
	file_mina |>
	readxl::read_xlsx() |>
	janitor::clean_names() |>
	mutate(success = as.factor(success)) |>
	mutate(across(chronic_lung_disease:icd_pm, ~ replace_na(.x, 0))) |>
	mutate(across(c(anti_arrhythmics, rate_controlling_agents, anticoagulants), ~ replace_na(.x, "None"))) 
	
	
lvidd <- glm(success ~ lvi_dd, family = "binomial", data = proc)

lvidd_ef <-
	glm(success ~ lvef + lvi_dd, family = "binomial", data = proc)

lvidd_la <-
	glm(success ~ la_vol_index + lvi_dd,
			family = "binomial",
			data = proc)

lvidd_la_ef <-
	glm(success ~ lvef + la_vol_index + lvi_dd,
			family = "binomial",
			data = proc) 

models <-	list(
	lvidd = lvidd,
	lvidd_ef = lvidd_ef,
	lvidd_la = lvidd_la,
	lvidd_la_ef = lvidd_la_ef
)
	
# Unadjusted
lvidd <- 
	tbl_regression(models$lvidd, exponentiate = TRUE) |>
	add_glance_source_note() 

# Adjusted for LVEF
lvidd_ef <-
	tbl_regression(models$lvidd_ef, exponentiate = TRUE) |>
	add_glance_source_note() 

# Adjusted for LA
lvidd_la <- 
	tbl_regression(models$lvidd_la, exponentiate = TRUE) |>
	add_glance_source_note() 

# Adjusted for all
lvidd_la_ef <- 
	tbl_regression(models$lvidd_la_ef, exponentiate = TRUE) |>
	add_glance_source_note() 

tbls <-
	list(
		lvidd = lvidd, 
		lvidd_ef = lvidd_ef, 
		lvidd_la = lvidd_la, 
		lvidd_la_ef = lvidd_la_ef
	)

```


class: center, middle, inverse
# Overview

---

### Objectives

1. Evaluate pilot data on TEE guided cardioversion

1. Efficacy of electrical cardioversion in atrial arrhythmias

1. Identify factors predisposing to successful cardioversion

1. Adjustment for clinical risk factors that would effect cardioversion success

---
class: center, middle, inverse
# Findings

---

```{r, demo}
proc |>
	select(success, age, gender, height, bmi, bsa) |>
	tbl_summary(
		by = success
	) |>
	add_overall() |>
	add_p()
```

---

```{r, echo}
proc |>
	select(success, type_of_arrhythmia, joules_used, la_diam, la_vol_index, lvef, lvi_dd) |>
	tbl_summary(
		by = success,
		missing = "no",
		type = c(joules_used, lvef, lvi_dd, la_vol_index, la_diam) ~ "continuous"
	) |>
	add_overall() |>
	add_p()
```

---

.pull-left[
```{r}
# Unadjusted
tbls$lvidd

# Adjusted for LVEF
tbls$lvidd_ef
```
]

.pull-right[
```{r}
# Adjusted for LA
tbls$lvidd_la

# Adjusted for all
tbls$lvidd_la_ef
```
]


